Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of abstract network topologies. We develop a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology. From such a specification, \sysname synthesizes a collection of router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
%
%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.

@@

We present \sysname, a system to generate provably-correct configuration templates. It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity. For instance, they may specify roles for ``top-of-rack'' and ``aggregation" routers and specify that every top-of-rack router connects to at least two aggregation routers (to tolerate the failure of a link to an aggregation router). Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate). For routing policy, we borrow notation from Propane~\cite{propane}, a language for specifying traffic paths at a high-level of abstraction. But while Propane policies
refer concrete devices, \sysname policies refer to abstract roles.

Based on these inputs, the \sysname compiler generates one template per role. It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that respects the abstraction, the resulting network will correctly implement the routing policy and meet the fault-tolerance requirements. To check fault-tolerance properties, we develop a new analysis over the abstraction based on a collection of inference rules about the number of disjoint paths between devices in different roles.

\sysname templates are also evolution-friendly. When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire a new neighboring device need to change (e.g., to activate a port on which the new device is connected).  No other device in the network is impacted.

>>>>

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of
abstract network topologies, and embody them in a network synthesis tool called
\sysname. \sysname allows network operators to write a high-level routing policy
over an abstraction of their network topology. From such a specification,
\sysname synthesizes a collection of router configurations running the
distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
centralized routing policy for any concrete instantiation of the abstract
topology, and for any combination of network failures in the resulting concrete
topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as
reachability between a source and destination under k-failures, are also
guaranteed to hold under any concrete instantiation of the abstract topology.
%
Something something, expandable/incremental networks. Something something scales
compilation to large networks. Something something, templates easier to
understand.
%These strong guarantees allow operators to reason about the routing behavior of
%their network at a high-level abstraction, while also generating an efficient
%low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any
%way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

We present \sysname, a system to generate provably-correct role templates. It
allows operators to input \emph{abstract network topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (e.g., the number of link failures
to tolerate). For routing policy, we borrow notation from
Propane~\cite{propane},  which specifies traffic paths at a high-level of
abstraction. But while Propane policies refer to concrete devices, \sysname
policies refer to abstract roles.

Based on these inputs, the \sysname compiler generates one template per role. It
guarantees that, when the templates are instantiated to configurations for {\em
any} concrete topology that complies with the abstract topology, the result
network will correctly implement the routing policy and meet the fault-tolerance
requirements. We show how fault-tolerance analysis can be done over abstract
topology itself using \todo{say something cool about about the inference rules
and such}.

\sysname templates are also evolution-friendly. When the network migrates from
one concrete topology to another, both of which comply with the abstract
topology, it is guaranteed that only the configurations of devices that acquire
or lose a neighboring device needs to change (e.g., to activate a port on which
the new device is connected).  No other device in the network is impacted.
